**Density Dependence**

### 2022-12-22 Rmd/runDD.Rmd
tested

---
title: "**Density Dependence**"
subtitle: "Simulations"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
mathjax: TRUE

>>>>

---
title: "**Density Dependence**"
subtitle: "Simulations"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE
